SSA based global code motion of identical computations

### 2017-04-15 acmart-pacmpl-template.tex
dj graph

Rosen et al. explain moving computations successors to remove redundancies
\cite{rosen1988global}. Their algorithm iterates on computations of same rank
and move the code with identical computations from the sibling branch. Also
there is no notion of partially hoisting the computations so their approach may
result in missing many hoisting opportunities.

@@

Shobaki \cite{shobaki2013} also recently presented a combinatorial global
scheduler with reasonable performance improvements. It is possible that both
Barany and Shobaki's implmentation will have similar results when compiled for
same target. Also, both suffer the same problem, although Shobaki not so much,
of large compile times which is not feasible for industrial compilers like gcc
and LLVM.

We got reduction in register spills on all the SPEC2006 benchmarks and
reasonable performance improvements with very low compile time overhead.

@@

The algorithm for code motion uses several common representations of the
program that we shortly describe below:
\begin{itemize}
\item Control Flow Graph (\CFG{}) and the Dominance (DOM) and Post-Dominance (PDOM)
  relations \cite{dragonbook};
\item Static Single Assignment (\SSA{}) \cite{cytron};
\item Global Value Numbering (\GVN{}) \cite{rosen1988global,click1995global}: to
  identify similar computations compilers use \GVN{}.  Each expression is given a
  unique number and the expressions that the compiler can prove identical are
  given the same number;
\item Memory \SSA{} \cite{novillo2007memory}: memory operations that the compiler
  is able to prove in dependence are linked through use-def chains.
\end{itemize}

@@

>>>>

Rosen \cite{rosen1988global} explain moving computations from successors. Their
algorithm iterates on computations of same rank and move the code with identical
computations from the sibling branch to a common dominator.

@@

Shobaki \cite{shobaki2013} also recently presented a combinatorial global
scheduler with reasonable performance improvements. It is possible that both
Barany and Shobaki's implmentation will have similar results when compiled for
same target. Also, both suffer from the same problem, although Shobaki not so
much, of large compile times which is not feasible for industrial compilers like
gcc and LLVM.

We got reduction in register spills on some SPEC2006 benchmarks, reduction in
code-size and some performance improvements with very low compile time overhead.

@@

The algorithm for code motion uses several common representations of the
program that we shortly describe below:
\begin{itemize}
\item Control Flow Graph (\CFG{}) and the Dominance (DOM) and Post-Dominance (PDOM)
  relations \cite{dragonbook};
\item DJ-Graph \cite{Sreedhar1996} is a data structure that augments the
  dominator tree with join-edges to keep track of data-flow in a program. We use
  DJ-Graph to compute liveness of variables as illustrated in \cite{das2012}.
\item Static Single Assignment (\SSA{}) \cite{cytron};
\item Global Value Numbering (\GVN{}) \cite{rosen1988global,click1995global}: to
  identify similar computations compilers use \GVN{}.  Each expression is given a
  unique number and the expressions that the compiler can prove identical are
  given the same number;
\item Memory \SSA{} \cite{novillo2007memory}: memory operations that the compiler
  is able to prove in dependence are linked through use-def chains.
\end{itemize}

@@

\subsection{Liveness using DJ Graph}
The DJ Graph is very useful for computing liveness because the values will only
flow either through dominator edges or the join edges (where we insert a PHI).
